Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-01 Paper/grass.tex

\begin{figure}
\includegraphics[scale=1]{Grass_Base_Nepf_shear}
\caption{Steady flow profile from the experiment of Ghisalberti\cite{Nepf04} (Case-I from Table-1 with 1250 plants/$m^2$, 
plant height = 13.7$\pm .2$cm and blade width of 0.64 cm)
 and it's approximation with $U_0=7.28$ cm/s and $\delta = 5.02$ cm with our model. The canopy extends upto $y=h_g$ in the water column of depth $2H$. 
The steady velocity profile can be decomposed into three regions, (i) A parabolic profile in the unvegetated region, (ii) a uniform profile deep within the grass bed, and (iii) a boundary layer of thicness $\delta$ near the canopy top. The depedence of the boundary layer on the vegetation density $\Ndg$ is shown in the inset and compared with our prediction.}
\label{fig:basicflow}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=1]{Grass_Base_Nepf_shear}
\caption{Steady flow profile from the experiment of Ghisalberti\cite{Nepf04} (Case-I from Table-1 with 1250 plants/$m^2$, 
plant height = 13.7$\pm .2$cm and blade width of 0.64 cm)
 and it's approximation with $U_0=7.28$ cm/s and $\delta = 5.02cm$ with our model. The canopy extends upto $y=h_g$ in the water column of depth $2H$. 
The steady velocity profile can be decomposed into three regions, (i) A parabolic profile in the unvegetated region, (ii) a uniform profile deep within the grass bed, and (iii) a boundary layer of thicness $\delta$ near the canopy top. The depedence of the boundary layer on the vegetation density $\Ndg$ is shown in the inset.}
\label{fig:basicflow}
\end{figure}
